---
title: "CHTC Facilitation Report"
author: "Christina Koch, Lauren Michael"
date: "Month Year"
output: 
  html_document
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(tidyr)

month <- '00'
year <- 2017
month_string <- "Month"
```

## Objectives

* Help researchers use CHTC’s resources for their research by guiding them through:
    * Designing computational approaches for best overall throughput, productivity, and research innovation
    * Submitting computational work to CHTC compute systems
    * Monitoring, troubleshooting, and debugging
    * Managing data in CHTC compute systems
* See: [New Engagements] + [Ongoing Support]

* Create a full set of online CHTC user guides and examples as an alternative/accompaniment to the user support described above, AND to replace the current, limited set of online materials.
* Provide in-person learning opportunities, not just for using CHTC computing resources, but in complement with other compute-related training on campus
* See: [Learning Resources]

* Establish connections and raise awareness of CHTC resources with other groups on campus
* Work with other individuals and organizations on campus who facilitate research computing via infrastructure, education, administration, etc.
* Work with other individuals and organizations on other campuses who facilitate research computing via infrastructure, education, etc.; share expertise, accomplish shared goals, create collaborations.
* See: [Partnerships]

## Engagments

### New Engagements

```{r eng_data}
# loading engagement data + counting new engagements
eng_data_file <- paste0('../data/mtgs/data/',year,'_',month,'.csv')
eng_data <- read.csv(eng_data_file,
                       header = TRUE, 
                       stringsAsFactors = FALSE)

new_eng_num <- eng_data %>% 
  filter(Type == 'initial') %>% 
  summarize(total = sum(Number))

oh_num <- eng_data %>%
    filter(Type == 'office hours') %>%
    distinct(Name) %>% summarize(total = sum(Number))

ongoing_num <- eng_data %>%
    filter(Type == 'ongoing') %>%
    distinct(Name) %>% summarize(total = sum(Number))
```

In `r month_string` CHTC Facilitators had initial 
meetings with `r new_eng_num[[1]]` researchers: 

```{r engagements}
eng_data %>%
    filter(Type == 'initial') %>%
    select(Name, Department) %>% 
    group_by(Department) %>%
    summarize(Names = paste(Name, collapse = ", ")) %>%
    arrange(Department) %>%
    select(Names, Department) %>%
    kable()
```

### Office Hours

There were `r oh_num[[1]]` researchers who attended office hours.  

```{r office}
eng_data %>%
    filter(Type == 'office hours') %>%
    select(Name, Department) %>% 
    distinct(Name) %>%
    group_by(Department) %>%
    summarize(Names = paste(Name, collapse = ", ")) %>%
    arrange(Department) %>%
    select(Names, Department) %>%
    kable()
```

### Ongoing Engagements

We had ongoing engagements with `r ongoing_num[[1]]` researchers.  

```{r ongoing}
eng_data %>%
    filter(Type == 'ongoing') %>%
    select(Name, Department) %>% 
    distinct(Name) %>%
    group_by(Department) %>%
    summarize(Names = paste(Name, collapse = ", ")) %>%
    arrange(Department) %>%
    select(Names, Department) %>%
    kable()
```

### Tickets

```{r tickets}
ticket_file <-  paste0('../data/tickets/data/tickets_',year,'-',month,'-01.csv')
ticket_data <- read.csv(ticket_file,
                       header = TRUE, 
                       stringsAsFactors = FALSE)
ticket_data <- ticket_data %>% filter(Owner == 'all')
```

Over the past month, CHTC facilitators and other staff
responded to `r ticket_data$Created` new support requests.  

### Highlights

> ADD HERE 

## Learning Resources

### Training

* Information here

### User Guides

* Information here

## Partnerships

### On Campus

* **Report stuff**
* Ongoing: 
    * 

### Off campus

* **Report stuff**
* Ongoing: 
    * Lauren is leading and both Christina and Lauren are participating in bi-weekly calls for ACI-REF[^6].  
    * Lauren is contributing to CaRC[^9] as an ACI-REF representative. 
    * Christina is continuing conversations with other interested researchers and staff members who would like to develop a Software Carpentry-like lesson for using large-scale compute systems.  
    * Christina continues to contribute to the Software[^2]/Data[^3] Carpentry organizations as an instructor trainer.  

## Other Impacts

* Any other campus impacts? 

## Staff Development

* Anything?

## Usage

```{r projects, include=FALSE}
hrs_data_file <- paste0('../data/hrs/data/clean/',year,'-',month,'_30_users.csv')
hrs_data <- read.csv(hrs_data_file)

chtc_users <- hrs_data %>%
  filter(CHTC_Supported > 0) %>%
  distinct(User) %>%
  tally()

chtc_projects <- hrs_data %>%
  filter(CHTC_Supported > 0) %>%
  distinct(Project) %>%
  tally()

chtc_depts <- hrs_data %>%
  filter(CHTC_Supported > 0) %>%
  distinct(Dept) %>%
  tally()
```

In `r month_string`, CHTC resources supported 

* `r chtc_users[[1]]` users
* in `r chtc_projects[[1]]` unique projects
* from `r chtc_depts[[1]]` departments.  

```{r top-users, include=FALSE}
print("Our top users were:")
hrs_data %>%
  filter(Project != 'icecube' & 
           Project != 'cms' & 
           Project != 'bmrb' & 
           Project != 'other' ) %>%
  select(User, Dept, CHTC_Supported) %>%
  arrange(-CHTC_Supported) %>%
  head() %>%
  kable()
```

```{r hours}
domain_data_file <- paste0('../data/hrs/data/clean/',year,'-',month,'_weekly.csv')
domain_hrs <- read.csv(domain_data_file)

tidy_hrs <- domain_hrs %>% 
  mutate(Domain = reorder(Domain, desc(CHTC_Supported))) %>%
  mutate(Flocking = CHTC_Supported - CHTC_Total) %>%
  select(-CHTC_Total, -Total, -CHTC_Supported) %>%
  gather(Hour_type, Hours, -Domain, -Week) %>%
  mutate(Hour_type = factor(Hour_type,
                            c("HPC","OSG","HTC",
                              "Flocking"))) 
tidy_hrs %>% 
  group_by(Week, Hour_type) %>%
  summarize(Hours = sum(Hours)) %>%
  ggplot(aes(x = Week, y = Hours, 
             group = Hour_type, color = Hour_type)) +
  geom_line(size = 1.2) + geom_point(size = 1.5) +
  theme_minimal() + ggtitle(paste0("CHTC Supported Hours in ",month_string))

domain_hrs %>% 
  mutate(Domain = reorder(Domain, desc(CHTC_Supported))) %>%
  mutate(Flocking = CHTC_Supported - CHTC_Total) %>%
  select(Domain, HTC, HPC, OSG, Flocking, CHTC_Supported) %>%
  group_by(Domain) %>%
  summarize_each(funs(sum)) %>%
  arrange(desc(CHTC_Supported)) %>% kable()


tidy_hrs %>%
  filter(Hour_type != 'CHTC_Total') %>%
  ggplot(aes(x = Week, y = Hours, 
             group = Hour_type, color = Hour_type)) +
  geom_line(size = 1.2) + geom_point(size = 1.5) +
  facet_wrap(~Domain) + 
  theme_minimal() + theme(axis.title.x=element_blank(),
                          axis.text.x=element_blank()) + 
  ggtitle(paste0("CHTC Supported Hours in ",month_string," by Domain"))
```

## List of Partners

[^1]: [Open Science Grid (OSG)](https://www.opensciencegrid.org/), national consortium of research organizations integrating high-throughput computing resources across the country (NSF-funded)
[^2]: [Software Carpentry](http://software-carpentry.org/), international non-profit organization providing computational instruction for researchers
[^3]: [Data Carpentry](http://www.datacarpentry.org/), international non-profit organization providing data management instruction for researchers
[^4]: [Morgridge Institute for Research (MIR)](https://morgridge.org/), private non-profit research institute
[^5]: [Wisconsin Institute for Discovery (WID)](http://wid.wisc.edu/), transdisciplinary campus research institute
[^6]: [Advanced Cyberinfrastructure Research and Education 
Facilitators (ACI-REF)](https://aciref.org/), national collaboration investigating the role of facilitation (NSF-funded)
[^7]: [HTCondor Project](http://research.cs.wisc.edu/htcondor/), project to develop the HTCondor software
[^8]: [Advanced Computing Initiative](http://aci.wisc.edu), task force reponsible for advising campus on research computing needs and direction
[^9]: Campus Research Computing (CaRC) Infrastructures Consortium, NSF research coordination network (RCN) project, creating a consortium of profesional communities around research computing on campuses
[^10]: [Campus Computing Infrastructure (CCI)](https://cci.wisc.edu/), group at UW Madison brokering computing and data services.  